Describing the C-space of asynchronous periodic task using DIT

### 2013-07-26 dit-paper_ieee.tex
- FPDIT calculation method

	The DBF allows to give a necessary and sufficient condition of feasibility:

@@

		Here, the possible values of $a_1$ are 3 and 4, and the possible values
		of $a_2$ are 7 and 8. For a FPDIT to exist, one of those
		condition must be fulfilled:
		\[
		\left[
		\begin{array}{c}
			3 + 0 \equiv 7 + 2 \; (\operatorname{mod} \; 4 ) \\
			3 + 0 \equiv 8 + 2 \; (\operatorname{mod} \; 4 ) \\
			4 + 0 \equiv 7 + 2 \; (\operatorname{mod} \; 4 ) \\
			4 + 0 \equiv 8 + 2 \; (\operatorname{mod} \; 4 ) \\
		\end{array}
		\right.
		\]
		However those four conditions are false, so the system has no FPDIT
		(and no other DIT than $t=0$).

	\subsection{Solving the modular system}

	PAUL PAUL PAUL ?

>>>>

	A necessary and sufficient condition of feasibility can easily be written
	based on the DBF:

@@

		Here, the possible values of $a_1$ are 3 and 4, and the possible values
		of $a_2$ are 7 and 8. For a FPDIT to exist, one of the following
		conditions must be fulfilled:
		\[
		\left[
		\begin{array}{c}
			3 + 0 \equiv 7 + 2 \; (\operatorname{mod} \; 4 ) \\
			3 + 0 \equiv 8 + 2 \; (\operatorname{mod} \; 4 ) \\
			4 + 0 \equiv 7 + 2 \; (\operatorname{mod} \; 4 ) \\
			4 + 0 \equiv 8 + 2 \; (\operatorname{mod} \; 4 ) \\
		\end{array}
		\right.
		\]
		However those four conditions cannot be satisfied, which means the system has
		no FPDIT (and no other DIT than $t=0$).

	\subsection{Solving the modular system}
		Finding the FPDIT of a system is similar to finding a synchronous instant of
		this system (an instant at which all tasks release a job simultaneously), but
		with weaker constraints. That is, the FPDIT is an instant after the last
		deadline of all tasks, but before the next arrival time of all tasks. Finding
		a synchronous instant is equivalent to finding a solution $t$ for the
		following set of constraints :
		\[
			\left\{
			\begin{array}{l}
				t \geqslant O_i \: \forall \: \tau_i \in \tau \\
				t \equiv O_i \; (mod \; T_i) \: \forall \: \tau_i \in \tau \\
			\end{array}
			\right.
		\]
		which is very similar to an instance of the Chinese Remainer Problem (CRP). It
		is not possible to directly use a solver for the CRP as in a task system,
		$T_i$ values could have common factors. However, the instance can be modified
		(each constraint with a non-prime period can be split into powers of primes
		without changing the solution if there is one) in order to make the problem
		solvable through applying a solution for the CRP. \\

		Now that we have a solver for the problem of finding a synchronous instant, we
		actually also have a solver for finding the FPDIT. The problem of finding the
		first DIT is the same as finding all the possible DIT then taking the minimum.
		Each of those DIT corresponds to a unique combination of $a_i$ values (one
		for each task). Finding one of such DIT is the same problem as finding a
		synchronous instant :
		\[
			\left\{
			\begin{array}{l}
				t \geqslant O_i + a_i \: \forall \: \tau_i \in \tau \\
				t \equiv O_i \; (mod \; T_i) \: \forall \: \tau_i \in \tau \\
			\end{array}
			\right.
		\]
		all DITs can be found by solving the equivalent CRP problem for all
		combinations of $a_i$ values. This is however very inefficient as there are
		exponentially many different combinations of $a_i$ values in the number of
		tasks.\\

		A better method for finding the FPDIT consists in splitting the algorithm that
		is used to solve the CRP in two separate parts. The algorithm requires
		calculating one modular inverse for each task.
